\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-07-27 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Amendement .tex

As in \cite{melitz}, firms are in monopolistic competition, each producing a differentiated variety using labor as sole production factor. Both countries being perfectly symmetric, the labor market equilibrium imposes the same wage in both countries, thus considered as the num\'{e}raire. Prices and costs are hence expressed in terms of labor. At entry, each firm pays a sunk entry cost $f_e$ and subsequently draws its productivity level $\varphi$ from a known distribution $G(\varphi)$. Production of $q$ units, a firm should employ $l(q|\varphi) = f+\frac{q}{\varphi}$ units of labor, with $f$ the fixed cost of production. Exporting is subject to an extra fixed cost $f_x$ and variable exporting costs of two types: an ad-valorem cost that depend on the value traded $\tau\geq 1$ and an additive cost depending on the quantity (weight) transported, $t\qeg 0$. \textbf{Mettre une footnote, unit vs weight}. At each point in time, a firm can be hit by a death shock at the exogenous probability $\delta>0$. Following \cite{melitz}, we solve the problem backwards. First, we solve for the maximizing profit behavior once entered. Second, we determine the entry conditions on the various markets.\medskip

@@

Making use of the firm's first-order pricing conditions, revenues on each local and export market respectively read as:
\begin{eqnarray}
% \nonumber % Remove numbering (before each equation)
  r_d(\varphi) &=& \left[\frac{1}{\rho } \frac{1}{\varphi}  \right]^{1-\sigma} P^{\sigma-1} E \label{eq:rd}\\
  r_x(\varphi) &=& \left[\frac{1}{\rho}\left(\frac{\tau}{\varphi} +t\right)  \right]^{1-\sigma} P^{\sigma-1} E \label{eq:rx}
\end{eqnarray}
\noindent with $\rho =  \frac{\sigma-1}{\sigma}$ inversely related to the markup.
\paragraph{Zero-cutoff profit conditions} Given the fixed costs on both the domestic and the export markets, only firms with a productivity above $\varphi^\ast$ will serve the domestic market, and those with $\varphi>\varphi_x^\ast$ will export abroad. The zero cut-off (ZCP) productivity level for successful entry on the domestic and export markets should verify:
\begin{eqnarray*}
\frac{\pi_d(\varphi^\ast)}{\delta} = 0 &\Leftrightarrow & \frac{r_d(\varphi^\ast)}{\sigma} - f =0\\
\frac{\pi_x(\varphi_x^\ast)}{\delta} = 0 &\Leftrightarrow & \frac{r_x(\varphi_x^\ast)}{\sigma} - f_x = 0
\end{eqnarray*}
\noindent with $\frac{\pi_d(\varphi^\ast)}{\delta}$ the expected profit on each market. Manipulating equations, we get:
\begin{eqnarray*}
% \nonumber % Remove numbering (before each equation)
  \varphi_x^\ast &=& \frac{\tau}{f_x^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}} -t} \\
  \varphi^\ast &=& \frac{1}{f_^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}}}
\end{eqnarray*}

@@

Following \cite{melitz}, and with $\Omega_d$, $\Omega_x$ the set of varieties respectively produced at Home and imported, one can then rewrite the price index (\ref{eq:CPI}) as:
\begin{eqnarray*}
P &=& \left[\int_{\omega \in \Omega_d} p_d^{1-\sigma}(\omega)d\omega + \int_{\omega \in \Omega_x} p_x^{1-\sigma}(\omega)d\omega  \right]^{\frac{1}{1-\sigma}} \\
&=& \left[\int_{0}^\infty p_d^{1-\sigma}(\varphi)M\mu(\varphi)d\varphi + \int_{0}^\infty p_x^{1-\sigma}(\varphi)M_x \mu_x(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}
\end{eqnarray*}
Making use of Equation (\ref{eq:muofphi}), the price index reads as:
\begin{eqnarray*}
P &=& \left[\frac{M}{1-G(\varphi^\ast)}\int_{\phi^\ast}^\infty p_d^{1-\sigma}(\varphi)g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty p_x^{1-\sigma}(\varphi)g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}} \\
\text{with}&& \left\{
\begin{array}{lll}
p_d(\varphi)&=& \frac{\sigma}{\sigma-1} \frac{1}{\varphi}\\
p_x(\varphi)&=& \frac{\sigma}{\sigma-1} \left[\frac{\tau}{\varphi} +t\right]
\end{array}
\right.
\end{eqnarray*}
Accordingly, the price index can be rewritten as:
$$P = \left(\frac{\sigma}{\sigma-1}\right)\left[\frac{M}{1-G(\varphi^\ast)}\int_{\phi^\ast}^\infty \phi^{\sigma-1}g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty \left[\varphi \left(\frac{\tau}{\tau+t \varphi}  \right)  \right]^{\sigma-1}g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}$$

Similarly as in the closed-economy case (\cite{melitz}), let us define $\widetilde{\varphi}(\varphi^\ast)$ and $\widetilde{\varphi}_x(\varphi_x^\ast)$ as the weighted average of productivities of the domestic firms, on the domestic market and the export market respectively:\footnote{In the symmetric two-country model, $\widetilde{\varphi}_x(\varphi_x^\ast)$ can also be defined as the weighted average of productivities of foreign exporters at Home, e.g. associated with the imported varieties.}

@@

Defining $\bar{\pi}$ as the average profit conditional to entry, this free-entry condition rewrites as:
\begin{equation}
\left(1-G(\varphi^\ast)\right)\frac{\bar{\pi}}{\delta} = f_e \label{eq:FEC}
\end{equation}
\noindent with $\left(1-G(\varphi^\ast)$ the probability of successful entry. In the open-economy setting, $\bar{\pi}$ can be expressed as:
$$\bar{pi} =\pi_d(\widetilde{\varphi}(\varphi^\ast)) + \rho_x \pi_x(\widetilde{\varphi}_x(\varphi_x^\ast))$$
\noindent with $\pi_d(\widetilde{\varphi}(\varphi^\ast)) \equiv \bar{pi}_d$ the average expected profit on the domestic market, $\pi_x(\widetilde{\varphi}_x(\varphi_x^\ast))\equiv \bar{pi^}_x$ the average expected export profit and $\rho_x$ the probability of exporting (conditional on entry on the domestic market), equal to:
$$\rho_x = \frac{1-G(\varphi_x^\ast)}{1-G(\varphi^\ast)}$$

@@

\paragraph{Summary} Equations (\ref{eq:def_phitilde}), (\ref{eq:def_phitildex}), (\ref{eq:ZCP}), (\ref{eq:link_thresholds}) and (\ref{eq:FEC}) determine a system of interdependent equations in five endogenous variables $\left\{\bar{\pi}, \widetilde{\varphi}, widetilde{\varphi}_x, \varphi^\ast, \varphi^\ast_x \right\}$, from which we can deduce the equilibrium values of the remaining set of variables (as detailed in Appendix \ref{app:theoretical_model}). Specifically, we will study the consequences of additive costs in terms of welfare, which can be shown to be the inverse of the price level as standard in this literature (the price level $P$ being given by Equation (\ref{eq:CPI_vf})).

@@

\subsection{General equilibrium}

@@

\subsection{Summary}

\subsubsection{General form}
Equations (\ref{eq:def_phitilde}), (\ref{eq:def_phitildex}), (\ref{eq:ZCP}), (\ref{eq:link_thresholds}) and (\ref{eq:FEC}) determine a system of interdependent equations in five endogenous variables $\left\{\bar{\pi}, \widetilde{\varphi}, \widetilde{\varphi}_x, \varphi^\ast, \varphi^\ast_x \right\}$. We can deduce the equilibrium values of the remaining set of variables $\left\{P, M_T, M, M_x, \widetilde{\varphi}_T, \bar{r} \right\}$ by recursively solving the following set of equations:

@@

>>>>

As in \cite{melitz}, firms are in monopolistic competition, each producing a differentiated variety using labor as sole production factor. Both countries being perfectly symmetric, the labor market equilibrium imposes the same wage in both countries, thus considered as the num\'{e}raire. Prices and costs are hence expressed in terms of labor. At entry, each firm pays a sunk entry cost $f_e$ and subsequently draws its productivity level $\varphi$ from a known distribution $G(\varphi)$. Production of $q$ units, a firm should employ $l(q|\varphi) = f+\frac{q}{\varphi}$ units of labor, with $f$ the fixed cost of production. Exporting is subject to an extra fixed cost $f_x$ and variable exporting costs of two types: an ad-valorem cost that depend on the value traded $\tau\geq 1$ and an additive cost depending on the quantity (weight) transported, $t\geq 0$. \textbf{Mettre une footnote, unit vs weight}. At each point in time, a firm can be hit by a death shock at the exogenous probability $\delta>0$. Following \cite{melitz}, we solve the problem backwards. First, we solve for the maximizing profit behavior once entered. Second, we determine the entry conditions on the various markets.\medskip

@@

Making use of the firm's first-order pricing conditions, revenues on each local and export market respectively read as:
\begin{eqnarray}
% \nonumber % Remove numbering (before each equation)
  r_d(\varphi) &=& \left[\frac{1}{\rho } \frac{1}{\varphi}  \right]^{1-\sigma} P^{\sigma-1} E \label{eq:rd}\\
  r_x(\varphi) &=& \left[\frac{1}{\rho}\left(\frac{\tau}{\varphi} +t\right)  \right]^{1-\sigma} P^{\sigma-1} E \label{eq:rx}
\end{eqnarray}
\noindent with $\rho =  \frac{\sigma-1}{\sigma}$ inversely related to the markup.
\paragraph{Zero-cutoff profit conditions} Given the fixed costs on both the domestic and the export markets, only firms with a productivity above $\varphi^\ast$ will serve the domestic market, and those with $\varphi>\varphi_x^\ast$ will export abroad. The zero cut-off (ZCP) productivity level for successful entry on the domestic and export markets should verify:
\begin{eqnarray*}
\frac{\pi_d(\varphi^\ast)}{\delta} = 0 &\Leftrightarrow & \frac{r_d(\varphi^\ast)}{\sigma} - f =0\\
\frac{\pi_x(\varphi_x^\ast)}{\delta} = 0 &\Leftrightarrow & \frac{r_x(\varphi_x^\ast)}{\sigma} - f_x = 0
\end{eqnarray*}
\noindent with $\frac{\pi_d(\varphi^\ast)}{\delta}$ the expected profit on each market. Manipulating equations, we get:
\begin{eqnarray*}
% \nonumber % Remove numbering (before each equation)
  \varphi_x^\ast &=& \frac{\tau}{f_x^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}} -t} \\
  \varphi^\ast &=& \frac{1}{f^{\frac{1}{1-\sigma}}B^{\frac{-1}{1-\sigma}}}
\end{eqnarray*}

@@

Following \cite{melitz}, and decomposing the set of available varieties into $\Omega_d$, $\Omega_x$ the set of varieties respectively produced at Home and imported, one can rewrite the price index (\ref{eq:CPI}) as:
\begin{eqnarray*}
P &=& \left[\int_{\omega \in \Omega_d} p_d^{1-\sigma}(\omega)d\omega + \int_{\omega \in \Omega_x} p_x^{1-\sigma}(\omega)d\omega  \right]^{\frac{1}{1-\sigma}} \\
&=& \left[\int_{0}^\infty p_d^{1-\sigma}(\varphi)M\mu(\varphi)d\varphi + \int_{0}^\infty p_x^{1-\sigma}(\varphi)M_x \mu_x(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}
\end{eqnarray*}
Making use of Equation (\ref{eq:muofphi}), the price index reads as:
\begin{eqnarray*}
P &=& \left[\frac{M}{1-G(\varphi^\ast)}\int_{\phi^\ast}^\infty p_d^{1-\sigma}(\varphi)g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty p_x^{1-\sigma}(\varphi)g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}} \\
\text{with}&& \left\{
\begin{array}{lll}
p_d(\varphi)&=& \frac{\sigma}{\sigma-1} \frac{1}{\varphi}\\
p_x(\varphi)&=& \frac{\sigma}{\sigma-1} \left[\frac{\tau}{\varphi} +t\right]
\end{array}
\right.
\end{eqnarray*}
Accordingly, the price index can be rewritten as:
$$P = \left(\frac{\sigma}{\sigma-1}\right)\left[\frac{M}{1-G(\varphi^\ast)}\int_{\phi^\ast}^\infty \phi^{\sigma-1}g(\varphi)d\varphi + \frac{M_x}{1-G(\varphi_x^\ast)}\int_{\varphi^\ast_x}^\infty \left[\varphi \left(\frac{\tau}{\tau+t \varphi}  \right)  \right]^{\sigma-1}g(\varphi)d\varphi  \right]^{\frac{1}{1-\sigma}}$$

Similarly as in the closed-economy case (\cite{melitz}), let us define $\widetilde{\varphi}(\varphi^\ast)$ and $\widetilde{\varphi}_x(\varphi_x^\ast)$ as the weighted average of productivities of the domestic firms, on the domestic market and the export market respectively:\footnote{In the symmetric two-country model, $\widetilde{\varphi}_x(\varphi_x^\ast)$ also corresponds to the weighted average of productivities of foreign exporters at Home, e.g. associated with the imported varieties.}

@@

Defining $\bar{\pi}$ as the average profit conditional to entry, this free-entry condition rewrites as:
\begin{equation}
\left(1-G(\varphi^\ast)\right)\frac{\bar{\pi}}{\delta} = f_e \label{eq:FEC}
\end{equation}

\noindent with $\left(1-G(\varphi^\ast)\right)$ the probability of successful entry. In the open-economy setting, $\bar{\pi}$ can be expressed as:
$$\bar{pi} =\pi_d(\widetilde{\varphi}(\varphi^\ast)) + \rho_x \pi_x(\widetilde{\varphi}_x(\varphi_x^\ast))$$
\noindent with $\pi_d(\widetilde{\varphi}(\varphi^\ast)) \equiv \bar{pi}_d$ the average expected profit on the domestic market, $\pi_x(\widetilde{\varphi}_x(\varphi_x^\ast))\equiv \bar{pi}_x$ the average expected export profit and $\rho_x$ the probability of exporting (conditional on entry on the domestic market), equal to:
$$\rho_x = \frac{1-G(\varphi_x^\ast)}{1-G(\varphi^\ast)}$$

@@

\paragraph{Summary} Equations (\ref{eq:def_phitilde}), (\ref{eq:def_phitildex}), (\ref{eq:ZCP}), (\ref{eq:link_thresholds}) and (\ref{eq:FEC}) determine a system of interdependent equations in five endogenous variables $\left\{\bar{\pi}, \widetilde{\varphi}, widetilde{\varphi}_x, \varphi^\ast, \varphi^\ast_x \right\}$. From this, we can deduce the equilibrium values of the remaining set of variables (as detailed in Appendix \ref{app:theoretical_model}). Specifically, we will study the consequences of additive costs in terms of welfare, which can be shown to be the inverse of the price level as standard in this literature (the price level $P$ being given by Equation (\ref{eq:CPI_vf})).

\subsection{Calibration}

As standard in this literature (\cite{Irrazabal_2015}, Melitz fial proofs), the heterogenity in firm productivity is assumed to be given by a Pareto distribution. In contrast to the standard case with only ad-valorem costs, the model can no longer be solved analytically due to the presence of additive costs (see Appendix \ref{app:theoretical_model}). In this case, we rely on the model's simulations to determine the steady state. This drives us to calibrate the structural parameters of the model. To do so, we rely on values commonly retained in the literature except for the two additive and ad-valorem transport costs, as reported in Table .
\begin{table}[htbp]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
\end{table}
The calibration of transport costs parameters relies on our empirical estimates. We notably illustrate the consequences of trade liberalization by comparing the equilibrium based on the 1974 values of transport costs (at the beginning of our sample), versus those of 2019 (at the very end of our estimation period), in both cases on only ad-valorem transport costs and in the presence of both additive and ad-valorem costs. Calibration of transport costs is displayed in Table \ref{tab:calib_TC}.

\begin{table}[htbp]
  \centering
  \caption{Calibration (2)}\label{tab:calib_TC}
\begin{center}
	\input{table_calibTC_combined.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{7pt}\footnotesize{Notes: TC = Transport Costs. In columns (1), (3), (5) and (7) only ad-valorem costs are considered. In Columns (2), (4), (6) and (8), we model both ad-valorem and additive costs. $t$ is calibrated so that the ratio $t/\widetilde{p}_x$ from the model matches its empirical target, with $widetilde{p}^{\text{fas}}_x$ the average fas price set in place by those domestic firms that export. We theoretically define the export fas price through: $p_x = \tau p^{\text{fas}} +t$}}}
\end{table}

@@

\subsection{Solving the general equilibrium}

@@

\subsubsection{Summary}

Equations (\ref{eq:def_phitilde}), (\ref{eq:def_phitildex}), (\ref{eq:ZCP}), (\ref{eq:link_thresholds}) and (\ref{eq:FEC}) determine a system of interdependent equations in five endogenous variables $\left\{\bar{\pi}, \widetilde{\varphi}, \widetilde{\varphi}_x, \varphi^\ast, \varphi^\ast_x \right\}$. We can deduce the equilibrium values of the remaining set of variables $\left\{P, M_T, M, M_x, \widetilde{\varphi}_T, \bar{r} \right\}$ by recursively solving the following set of equations:

@@

\subsection{With a Pareto distribution}

As in most of the related literature (\cite{Irrazabal_2015}, \textbf{Melitz final proofs}, ...), we adopt a Pareto distribution for firm productivity heterogeneity, with the density and the cumulative functions respectively written as:
\begin{eqnarray*}
g(\varphi) &=& k\varphi_{\text{min}}^k \varphi^{-(k+1)}\\
G(\varphi) &=& 1 -\left( \frac{\varphi_{\text{min}}}{\varphi} \right)^k
\end{eqnarray*}

With the Pareto distribution, the system of Equations (\ref{eq:def_phitilde}), (\ref{eq:def_phitildex}), (\ref{eq:ZCP}), (\ref{eq:link_thresholds}) and (\ref{eq:FEC}) can be rewritten as a system of four equations in four endogenous variables: $\left\{\bar{pi}, g(\varphi_x^\ast),\varphi_x^\ast, \varphi^\ast  \right\}$ as given by:

\begin{eqnarray}
\bar{\pi}&=& \frac{\sigma-1}{k-(\sigma-1)}f + \left(\varphi^\ast \right)^k f_x\left[k\left(\frac{\tau}{\varphi_x^\ast}+t  \right)^{\sigma-1}\left[  1+(k(\varphi_x^\ast)^k g(\varphi_x^\ast))^{\frac{1}{\sigma-1}}\right]^{1-\sigma}  - \left( \varphi_x^\ast \right)^{-k} \right] \label{eq:systemPareto_1}\\
g(\varphi_x^\ast)&=&\int_{\varphi_x^\ast}^\infty \varphi^{\sigma-1-(k+1)}(\tau +t\varphi)^{1-\sigma}d\varphi \label{eq:systemPareto_2}\\
\frac{\varphi_x^\ast}{\tau+ t\varphi_x^\ast}&=&\varphi^\ast \left[ \frac{f}{f_x} \right]^{\frac{1}{1-\sigma}} \label{eq:systemPareto_3}\\
\bar{\pi}&=& \delta f_e \left( \frac{\varphi^\ast}{\varphi_{\text{min}}} \right)^k \label{eq:systemPareto_4}
\end{eqnarray}

Notice that, in the absence of additive costs ($t=0$), Equation (\ref{eq:systemPareto_2}) rewrites as:
$$g(\varphi_x^\ast) = \tau^{1-\sigma}\left[ \frac{(\varphi_x^\ast)^{-(k-(\sigma-1))}}{k-(\sigma-1)}\right]$$
The system of Equations (\ref{eq:systemPareto_1})-((\ref{eq:systemPareto_4}) thus simplifies to be solved recursively with a full analytical solution. This is no longer the case in the presence of additive costs, and we have to rely on the model's simulations to obtain the general equilibrium of the model for a given calibration of the deep parameters.
